\documentclass[titlepage]{report}

\usepackage{setspace}

\usepackage[utf8]{inputenc}
\usepackage{amsmath}   
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage{hyperref}
\usepackage{listings}
\usepackage[labelfont=bf]{caption}
\usepackage[margin=3.5cm]{geometry}

%\usepackage{qtree}
%\usepackage{tikz}
%\usepackage{tikz-qtree}

%\usepackage[]{algorithm2e}

\lstset{
	basicstyle=\footnotesize\ttfamily,
}

\title{
\vspace{80pt}\\
\LARGE \bfseries SKEDGE
\\\vspace{10pt}\Large Smarter course scheduling for our\\University of Rochester
}

\author{
	Dan Hassin\\
    \vspace{5pt}\\
    Supervised by Professor Philip Guo\\
    \vspace{5pt}\\
    Department of Computer Science\\
    University of Rochester\\
    Rochester, New York\\
}

\date{April 12, 2016\\
    \vspace{150pt}\\
    submitted in partial fulfillment of\\
    the requirements for the degree\\
    honors bachelor of science\\
}

\begin{document}

\maketitle

\doublespacing

% Direct search for specific course
% Discovery, browsing, exploring
% behavioral patterns

% STAT: Find major of users, find how many non-major courses they found

\begin{abstract}

In this paper I present Skedge, a web application for students to comfortably and effectively engage with the University's course catalog. Skedge matches and surpasses the capabilities of the existing University tool for this purpose, ``Course Description / Course Schedule'' (CDCS) and presents its information in a more visually pleasing way. As a result, Skedge boasts strong user-retention rates, long session durations, and high student adoption despite having virtually no advertisement. Through collected usage data, I demonstrate that a) Skedge's differences from and additions to CDCS are usable and have real need, b) the two major use-cases associated with course browsing---direct search and exploratory search---are effectively accommodated by Skedge, and c) Skedge's search mechanism is user-friendly and self-teaches to users over time.

\end{abstract}

\tableofcontents

\include{01-introduction}
\clearpage

\include{02-grievances}
\clearpage

\include{03-analytics}
\clearpage

\include{04-conclusion}
\clearpage

\begin{thebibliography}{1}

	\bibitem{esprima} Ariya Hidayat {\em Esprima}
		\\\url{http://esprima.org/}

	\bibitem{markov} Takis Konstantopoulos {\em Introductory lecture notes on
		Markov Chains and Random Walks.} Uppsala University,
		\\\url{http://www2.math.uu.se/~takis/L/McRw/mcrw.pdf}

	\bibitem{hosa} Frank Pfenning, Conal Elliott
		{\em Higher-Order Abstract Syntax.}
		ACM SIGPLAN Notices. Vol. 23. No. 7. ACM, 1988.
		\\\url{http://www.cs.cmu.edu/~fp/papers/pldi88.pdf}

	\bibitem{escodegen} Yusuke Suzuki {\em Escodegen}
		\\\url{https://github.com/Constellation/escodegen}

	\bibitem{parser api} Mozilla Developer Network {\em SpiderMonkey Parser API}
		\\\url{https://developer.mozilla.org/en-US/docs/SpiderMonkey/Parser_API}

\end{thebibliography}

\addcontentsline{toc}{part}{Bibliography}

\clearpage
\section*{Appendix}

\end{document}
